---
title:        "README"
bibliography: inst/REFERENCES.bib
csl:          inst/apa.csl
output:       github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PublicationBiasBenchmark

An R package for benchmarking publication bias correction methods through simulation studies.

## Installation

```{r, eval = FALSE}
# Install from GitHub
devtools::install_github("FBartos/PublicationBiasBenchmark")
```

## Usage


### Simulating From Existing Data Generating Models

```r

# Obtain a data.frame with pre-defined conditions
dgm_conditions("Stanley2017)

# simulate the data from the second condition
df <- simulate_dgm("Stanley2017", 2)

# fit a method
run_method("RMA", df)
```


### Using Pre-Simulated Datasets

```r 

# download the pre-simulated datasets to "sims" folder
download_folder <- file.path(getwd(), "sims")
download_dgm_datasets("no_bias", path = download_folder)

# retrieve first repetition of first condition from the downloaded datasets
retrieve_dgm_dataset("no_bias", condition_id = 1, repetition_id = 1, path = download_folder)

```

### Simulating From Existing DGM With Custom Settings

```r

# define sim setting
sim_settings <- list(
  n_studies     = 100,
  mean_effect   = 0.3,
  heterogeneity = 0.1
)

# check whether it is feasible
# (defined outside of the function - not to decrease performance during simulation)
validate_dgm_setting("no_bias", sim_settings)

# simulate the data
df <- simulate_dgm("no_bias", sim_settings)

# fit a method
run_method("RMA", df)
```

### Key Functions

#### Data Generating Mechanisms
- `simulate_dgm()`: Generates simulated data according to specified data generating model and settings.
- `dgm_conditions()`: Lists prespecified conditions of the data generating mechanism.
- `validate_dgm_setting()`: Validates (custom) setting of the data generating mechanism.
- `download_dgm_datasets()`: Downloads pre-simulated datasets from the OSF repository.
- `retrieve_dgm_dataset()`: Retrieves the condition and repetition of the pre-simulated dataset downloaded from the OSF repository.

#### Method Estimation
- `run_method()`: Estimates method on a supplied data according to the specified settings.
- `method_settings()`: Lists prespecified settings of the method.

### Available DGM Models

See `methods("dgm")` for the full list:

- `"no_bias"`: Generates data without publication bias (a test simulation)
- `"Stanley2017"`: @stanley2017finding
- `"Alinaghi2018"`: @alinaghi2018meta
- `"Bom2019"`: @bom2019kinked
- `"Carter2019"`: @carter2019correcting

### Available Methods

See `methods("method")` for the full list:

- `"RMA"`: Random effects meta-analysis
- `"PET"`: Precision-Effect Test (PET) publication bias adjustment [@stanley2014meta]
- `"PEESE"`: Precision-Effect Estimate with Standard Errors (PEESE) publication bias adjustment [@stanley2014meta]
- `"PETPEESE"`: Precision-Effect Test and Precision-Effect Estimate with Standard Errors (PET-PEESE) publication bias adjustment [@stanley2014meta]
- ...

### DGM OSF Repositories
All DGM are linked within the OSF repository () and contain the following elements:

- `data` : folder containing by-condition simulated datasets for all repetitions
- `results` : folder containing by-method results for all conditions * repetitions
- `metadata` : folder containing the following information:
  - `conditions.csv` : file mapping of all conditions and the corresponding settings
  - `data_generation.R` : file with code and reproducibility details for exact reproduction of the pre-simulated datasets
  - `methods.R` : file with code and reproducibility details for exact reproduction of the by method results


### References
