---
title: "Benchmark Releases"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Benchmark Releases}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

Each benchmark release is a complete catalog of independently downloadable units.
The installed package pins a default release. Archive-backed releases upload only
new or corrected units and import unchanged ZIPs into native Zenodo versions. Cite the
catalog record's version DOI, available from `list_benchmark_releases()`, and
record the benchmark release you used.

## Download exactly what you need

```{r}
library(PublicationBiasBenchmark)
PublicationBiasBenchmark.options(resources_directory = "resources")
list_benchmark_releases()
release <- "2026.1"

# One DGM's simulated datasets, including all repetitions.
download_dgm_datasets("no_bias", release = release)
dataset <- retrieve_dgm_dataset("no_bias", condition_id = 1,
                                repetition_id = 1, release = release)

# One DGM and method's raw results. All distributed shards are combined.
download_dgm_results("no_bias", method = "RMA", release = release)
results <- retrieve_dgm_results("no_bias", method = "RMA", release = release)

# One DGM and method's measures. No other methods' tables are downloaded.
download_dgm_measures("no_bias", method = "RMA", release = release)
measures <- retrieve_dgm_measures("no_bias", method = "RMA", release = release)
```

Release `2026.1` uses direct CSV downloads (catalog schema 1). Schema-2 releases
use one storage family per DGM, with separate ZIPs for datasets, each method/setting's
results, each method/setting's measures, metadata and the original source archive.
Ordinary and replacement measures share a ZIP; pairwise tables require an explicit
`measure = "pairwise"` selection. Individual distributed CSV shards keep their
original bytes inside each ZIP and are combined by the retrieval functions.

A dataset condition filter can download other conditions in its containing ZIP,
potentially all of a small DGM's datasets. A measure filter can download other
measure columns and both replacement variants for the selected method/setting.
These downloads never include another DGM's datasets or another method's ordinary
results/measures. Sharing a Zenodo record never forces downloading its other ZIPs.
ZIPs are capped at 2,000,000,000 uncompressed bytes and split at file boundaries.
An individual larger file must be prepared as smaller worker shards.

```{r}
list_benchmark_resources(release, "no_bias", "results", method = "RMA")
verify_benchmark_resources(release, "no_bias", "results", method = "RMA")
catalog <- benchmark_catalog(release)
benchmark_conditions("no_bias", release)
```

The catalog pins the condition definitions, file hashes, producing package version
when known, and source provenance. Historical generation versions remain unknown
where the archive does not establish them. The package version assembling a
release is recorded separately. Existing method/version fields inside results
remain authoritative.

The cache contains `releases/<release>/release.json`,
`cache/<sha256>/<filename>` and, for schema 2, `archives/<sha256>/<zipname>`.
Readers use the selected catalog and verify cached
bytes before reading. Reusing a resources directory across package versions is
safe: unrelated files are never included by scanning the cache. An incomplete
download, an overlapping shard, or a requested unavailable condition/repetition
raises an error. Download functions repair corrupt members from a cached ZIP when
possible. Existing verified `2026.1` member caches avoid new archive downloads.
`prune_benchmark_archives(release)` reports ZIPs whose selected members are all
verified; `dry_run = FALSE` removes those ZIP copies to reclaim disk space.

The [project community](https://zenodo.org/communities/publicationbiasbenchmark/)
provides navigation and curation. Use the exact release catalog version DOI when
citing an analysis. The catalog concept DOI leads to the latest release. Catalog
`hasPart` links identify exact storage versions; storage `isPartOf` links identify
the catalog concept. Public downloads require no token or community membership.

## Publish distributed computations

Workers write unpublished files beneath `resources_directory/DGM/results`. A CSV
shard contains one method and setting, and has unique condition/repetition keys.
Workers must use disjoint keys; report the package version that actually generated
each batch. Use `source = "local"` with result readers, and
`results_source = "local"` when computing measures from these unpublished files.
Publishing is done by a maintainer after the workers finish.

```{r}
# Describe individual worker outputs without combining them.
files <- list(
  benchmark_resource("worker-01.csv", "no_bias", "results",
    method = "myMethod", method_setting = "default", package_version = "0.4.0",
    id = "no_bias/results/myMethod-default/batch-01"),
  benchmark_resource("worker-02.csv", "no_bias", "results",
    method = "myMethod", method_setting = "default", package_version = "0.4.0",
    id = "no_bias/results/myMethod-default/batch-02")
)

# Alternatively, discover local shards and split locally computed measures.
files <- prepare_benchmark_resources("no_bias", kinds = c("results", "measures"),
  output_directory = "resources/prepared", package_version = "0.4.0")

metadata <- list(
  creators = list(list(person_or_org = list(type = "personal",
    given_name = "Your", family_name = "Name"))),
  rights = list(list(id = "cc-by-4.0"))
)
plan <- plan_benchmark_release("my-next-release", files, previous = "2026.1",
  metadata = metadata, state_directory = "resources/publication/my-next-release",
  catalog_record_id = "23070787", catalog_concept_doi = "10.5281/zenodo.23070786")
benchmark_packing_report(plan)

# ZENODO_TOKEN is read from the environment, never saved into state.
stage_benchmark_release(plan)
verify_benchmark_release(plan)
entry <- publish_benchmark_release(plan)
```

Keep publication state for retries. Running the same plan again resumes pending
uploads, verifies completed files, and recovers published records after lost
responses. Files in completed drafts are never replaced when their hashes differ.
Staging initializes new files in batches, reuses empty pending entries, and honors
Zenodo's rate-limit wait headers. Other uncertain failures are recovered by running
the same plan again.
Archive bytes are built once with the suggested `zip` package and persisted with
their hashes for retries. Only flat ASCII regular-file members using store or
deflate compression are supported; the reader checks the ZIP central directory,
including link attributes, before extracting. A new DGM storage version imports
the previous version's files, removes superseded unit ZIPs from the new draft, and
uploads complete replacement ZIPs. Imported ZIPs count toward the 100-file and
50,000,000,000-byte default limits. Packing fails instead of creating arbitrary
extra record families. `archive = FALSE` retains the legacy direct-file publisher.

The catalog is published only after complete public archive and member verification
and accepted community inclusion. The publisher submits published records and
accepts its own inclusion requests with the community owner's token; it preserves
the community review policy. Subsequent storage and catalog versions inherit the
family's community membership and branding, which are checked on every release.
Catalog publication continues the existing native version family with a new DOI.
`update_benchmark_community_pages()` is a separate, explicit operation for reviewed
About and curation HTML. It preserves the community's access and review policies.

A correction to an existing logical shard requires its ID in `replace`. The new
catalog selects corrected bytes; earlier catalogs retain the old references. Frozen
conditions and dataset coverage cannot grow for an existing DGM. Add a new DGM
identifier for new conditions or datasets. Corrections of existing dataset assets
are allowed explicitly, but affected results and derived measures must be
recomputed, supplied and listed in `replace` in the same release. Result corrections
or additions invalidate affected ordinary, replacement and pairwise measures.
The publisher records input asset IDs/hashes and rejects stale derived assets.
Provide actual input IDs through `benchmark_resource(dependencies = ...)` when
known; otherwise coverage and method metadata conservatively infer dependencies.
Metadata and source archive assets can be explicitly corrected, but new assets
of these kinds require a new DGM. Generation versions remain attached to members;
the package version building a ZIP is recorded separately.

Use `ZENODO_SANDBOX_TOKEN` with `sandbox = TRUE` and a dedicated sandbox community
for integration tests; the production community UUID does not exist there.
Before production publication, review the persisted packing report, complete
asset audit, proposed metadata and sandbox evidence. Production writes and the
subsequent package-default switch have separate user approval checkpoints.

After verified publication and approval, add `entry` to `inst/extdata/benchmark-releases.json` and set
`default_release` for the next package release. A catalog file can also be used
directly with `release = "/path/to/release.json"`. Concurrent publishers must use
distinct release identifiers; only one maintainer publishes a given plan.

## OSF baseline

The verified baseline is [release 2026.1](https://doi.org/10.5281/zenodo.23070787),
the default benchmark release in package version 0.4.0. Its catalog references
2,216 files across 40 component records (28.098 GB), including all 1,965 original
OSF files. The catalog is a separate Zenodo record.

The migration retains every original OSF file and source hash. Original mixed
method measure tables remain in `archive`; per-method tables provide the public
reader interface. Canonical frozen conditions repair a truncated Bom2019 CSV and
misassigned Carter2019 metadata. Four WILS example files had `method_setting`
incorrectly labelled `default`; explicit corrected files preserve every numerical
token, and the original files remain archived. The worker mapping, archived
measures and reproduced fits establish the example setting. No archived numerical
results are recalculated as part of migration.

The one-off migration scripts and source copies are retained locally outside Git.
Subsequent releases use the package's preparation and publication functions shown
above. Keep the publication state directory until public verification and registry
pinning finish; it allows an interrupted upload to resume without replacing
completed files.
