---
title: "Benchmark Releases"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Benchmark Releases}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

Each benchmark release is a complete catalog of separately downloadable files.
The installed package pins a default release. A new release uploads only new or
corrected files and refers to unchanged files in earlier Zenodo records. Cite the
catalog record's version DOI, available from `list_benchmark_releases()`, and
record the benchmark release you used.

## Download exactly what you need

```{r}
library(PublicationBiasBenchmark)
PublicationBiasBenchmark.options(resources_directory = "resources")
list_benchmark_releases()
release <- "2026.1"

# One DGM's simulated datasets, including all repetitions.
download_dgm_datasets("no_bias", release = release)
dataset <- retrieve_dgm_dataset("no_bias", condition_id = 1,
                                repetition_id = 1, release = release)

# One DGM and method's raw results. All distributed shards are combined.
download_dgm_results("no_bias", method = "RMA", release = release)
results <- retrieve_dgm_results("no_bias", method = "RMA", release = release)

# One DGM and method's measures. No other methods' tables are downloaded.
download_dgm_measures("no_bias", method = "RMA", release = release)
measures <- retrieve_dgm_measures("no_bias", method = "RMA", release = release)
```

Dataset files are partitioned by condition. Results are partitioned by method
and setting, with separate files allowed for distributed jobs. Measures are wide
tables partitioned by method and setting, with separate ordinary and replacement
variants. Downloading a measure such as bias can fetch that method's other measure
columns; it never fetches another method's results or measures. Metadata and the
unaltered OSF archive are separate resource kinds.

Zenodo records are storage containers, not download bundles. The package packs
files into additional records as the file-count or byte limit is reached. Sharing
a record never forces users to download its other files.

```{r}
list_benchmark_resources(release, "no_bias", "results", method = "RMA")
verify_benchmark_resources(release, "no_bias", "results", method = "RMA")
catalog <- benchmark_catalog(release)
benchmark_conditions("no_bias", release)
```

The catalog pins the condition definitions, file hashes, producing package version
when known, and source provenance. Historical generation versions remain unknown
where the archive does not establish them. The package version assembling a
release is recorded separately. Existing method/version fields inside results
remain authoritative.

The cache contains `releases/<release>/release.json` and
`cache/<sha256>/<filename>`. Readers use the selected catalog and verify cached
bytes before reading. Reusing a resources directory across package versions is
safe: unrelated files are never included by scanning the cache. An incomplete
download, an overlapping shard, or a requested unavailable condition/repetition
raises an error. Download functions repair corrupt cached files automatically.

## Publish distributed computations

Workers write unpublished files beneath `resources_directory/DGM/results`. A CSV
shard contains one method and setting, and has unique condition/repetition keys.
Workers must use disjoint keys; report the package version that actually generated
each batch. Use `source = "local"` with result readers, and
`results_source = "local"` when computing measures from these unpublished files.
Publishing is done by a maintainer after the workers finish.

```{r}
# Describe individual worker outputs without combining them.
files <- list(
  benchmark_resource("worker-01.csv", "no_bias", "results",
    method = "myMethod", method_setting = "default", package_version = "0.4.0",
    id = "no_bias/results/myMethod-default/batch-01"),
  benchmark_resource("worker-02.csv", "no_bias", "results",
    method = "myMethod", method_setting = "default", package_version = "0.4.0",
    id = "no_bias/results/myMethod-default/batch-02")
)

# Alternatively, discover local shards and split locally computed measures.
files <- prepare_benchmark_resources("no_bias", kinds = c("results", "measures"),
  output_directory = "resources/prepared", package_version = "0.4.0")

metadata <- list(
  creators = list(list(person_or_org = list(type = "personal",
    given_name = "Your", family_name = "Name"))),
  licenses = list(list(id = "cc-by-4.0"))
)
plan <- plan_benchmark_release("2026.2", files, previous = "2026.1",
  metadata = metadata, state_directory = "resources/publication/2026.2")
lengths(plan$groups) # files per new component record

# ZENODO_TOKEN is read from the environment, never saved into state.
stage_benchmark_release(plan)
verify_benchmark_release(plan)
entry <- publish_benchmark_release(plan)
```

Keep publication state for retries. Running the same plan again resumes pending
uploads, verifies completed files, and recovers published records after lost
responses. Files in completed drafts are never replaced when their hashes differ.
Staging initializes new files in batches, reuses empty pending entries, and honors
Zenodo's rate-limit wait headers. Other uncertain failures are recovered by running
the same plan again.
The catalog is published only after every new component's public bytes pass both
SHA-256 and MD5 verification. Publication creates a new catalog DOI; it does not
overwrite a previous record.

A correction to an existing logical shard requires its ID in `replace`. The new
catalog selects corrected bytes; earlier catalogs retain the old references. Frozen
condition definitions cannot change for existing IDs. Add a new DGM identifier if
a definition changes. Replacement measures that depend on a corrected result
must be recomputed and explicitly replaced as part of the same release.

After publication, add `entry` to `inst/extdata/benchmark-releases.json` and set
`default_release` for the next package release. A catalog file can also be used
directly with `release = "/path/to/release.json"`. Concurrent publishers must use
distinct release identifiers; only one maintainer publishes a given plan.

## OSF baseline

The verified baseline is [release 2026.1](https://doi.org/10.5281/zenodo.23070787),
the default benchmark release in package version 0.4.0. Its catalog references
2,216 files across 40 component records (28.098 GB), including all 1,965 original
OSF files. The catalog is a separate Zenodo record.

The migration retains every original OSF file and source hash. Original mixed
method measure tables remain in `archive`; per-method tables provide the public
reader interface. Canonical frozen conditions repair a truncated Bom2019 CSV and
misassigned Carter2019 metadata. Four WILS example files had `method_setting`
incorrectly labelled `default`; explicit corrected files preserve every numerical
token, and the original files remain archived. The worker mapping, archived
measures and reproduced fits establish the example setting. No archived numerical
results are recalculated as part of migration.

The one-off migration scripts and source copies are retained locally outside Git.
Subsequent releases use the package's preparation and publication functions shown
above. Keep the publication state directory until public verification and registry
pinning finish; it allows an interrupted upload to resume without replacing
completed files.
