---
title: "Results: Alinaghi (2018)"
output: html_document
vignette: >
  %\VignetteIndexEntry{Results: Alinaghi (2018)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
this_dir <- dirname(knitr::current_input(dir = TRUE))
source(file.path(this_dir, "_functions.R"))
dgm_names    <- "Alinaghi2018"
common_scale <- TRUE
```

## Complete Results

```{r, child = child_path("_results-main.Rmd")}
```


## Subset: Fixed Effects

`r paste0(generic_overview_text(dgm_names, results_conditional[results_conditional$condition_id %in% conditions$condition_id[conditions$environment == "FE"],])) `

### Average Performance {.tabset .tabset-fade .tabset-pills}

```{r, include = FALSE}
# compute average performance
this_tables_conditional <- make_table_summary(results_conditional[results_conditional$condition_id %in% conditions$condition_id[conditions$environment == "FE"],], common_scale = TRUE)
this_tables_replacement <- make_table_summary(results_replacement[results_replacement$condition_id %in% conditions$condition_id[conditions$environment == "FE"],], common_scale = TRUE)

# add ranks
this_rankings_conditional <- make_rank_summary(this_tables_conditional)
this_rankings_replacement <- make_rank_summary(this_tables_replacement)
```
```{r, child = child_path("_results-tabs-tables.Rmd")}
```


### By-Condition Performance (Conditional on Method Convergence) {.tabset .tabset-fade .tabset-pills}

`r paste0(conditional_text())`

```{r, include = FALSE}
  this_results <- results_conditional[results_conditional$condition_id %in% conditions$condition_id[conditions$environment == "FE"],]
```
```{r, child = child_path("_results-tabs-figures.Rmd")}
```


### By-Condition Performance (Replacement in Case of Non-Convergence) {.tabset .tabset-fade .tabset-pills}

`r paste0(method_replacement_text())`

```{r, include = FALSE}
  this_results <- results_replacement[results_replacement$condition_id %in% conditions$condition_id[conditions$environment == "FE"],]
```
```{r, child = child_path("_results-tabs-figures.Rmd")}
```

## Subset: Random Effects

`r paste0(generic_overview_text(dgm_names, results_conditional[results_conditional$condition_id %in% conditions$condition_id[conditions$environment == "RE"],])) `

### Average Performance {.tabset .tabset-fade .tabset-pills}

```{r, include = FALSE}
# compute average performance
this_tables_conditional <- make_table_summary(results_conditional[results_conditional$condition_id %in% conditions$condition_id[conditions$environment == "RE"],], common_scale = TRUE)
this_tables_replacement <- make_table_summary(results_replacement[results_replacement$condition_id %in% conditions$condition_id[conditions$environment == "RE"],], common_scale = TRUE)

# add ranks
this_rankings_conditional <- make_rank_summary(this_tables_conditional)
this_rankings_replacement <- make_rank_summary(this_tables_replacement)
```
```{r, child = child_path("_results-tabs-tables.Rmd")}
```


### By-Condition Performance (Conditional on Method Convergence) {.tabset .tabset-fade .tabset-pills}

`r paste0(conditional_text())`

```{r, include = FALSE}
  this_results <- results_conditional[results_conditional$condition_id %in% conditions$condition_id[conditions$environment == "RE"],]
```
```{r, child = child_path("_results-tabs-figures.Rmd")}
```


### By-Condition Performance (Replacement in Case of Non-Convergence) {.tabset .tabset-fade .tabset-pills}

`r paste0(method_replacement_text())`

```{r, include = FALSE}
  this_results <- results_replacement[results_replacement$condition_id %in% conditions$condition_id[conditions$environment == "RE"],]
```
```{r, child = child_path("_results-tabs-figures.Rmd")}
```

## Subset: Panel Random Effects

`r paste0(generic_overview_text(dgm_names, results_conditional[results_conditional$condition_id %in% conditions$condition_id[conditions$environment == "PRE"],])) `

### Average Performance {.tabset .tabset-fade .tabset-pills}

```{r, include = FALSE}
# compute average performance
this_tables_conditional <- make_table_summary(results_conditional[results_conditional$condition_id %in% conditions$condition_id[conditions$environment == "PRE"],], common_scale = TRUE)
this_tables_replacement <- make_table_summary(results_replacement[results_replacement$condition_id %in% conditions$condition_id[conditions$environment == "PRE"],], common_scale = TRUE)

# add ranks
this_rankings_conditional <- make_rank_summary(this_tables_conditional)
this_rankings_replacement <- make_rank_summary(this_tables_replacement)
```
```{r, child = child_path("_results-tabs-tables.Rmd")}
```


### By-Condition Performance (Conditional on Method Convergence) {.tabset .tabset-fade .tabset-pills}

`r paste0(conditional_text())`

```{r, include = FALSE}
  this_results <- results_conditional[results_conditional$condition_id %in% conditions$condition_id[conditions$environment == "PRE"],]
```
```{r, child = child_path("_results-tabs-figures.Rmd")}
```


### By-Condition Performance (Replacement in Case of Non-Convergence) {.tabset .tabset-fade .tabset-pills}

`r paste0(method_replacement_text())`

```{r, include = FALSE}
  this_results <- results_replacement[results_replacement$condition_id %in% conditions$condition_id[conditions$environment == "PRE"],]
```
```{r, child = child_path("_results-tabs-figures.Rmd")}
```



```{r, child = child_path("_results-sessionInfo.Rmd")}
```
